\ \\ \LARGE\bf Speculative Evaluation in Particle Swarm Optimization \thanks{Matthew Gardner, Andrew McNabb, and Kevin Seppi are with the Department of Computer Science, Brigham Young University, 3361 TMCB, Provo, UT 84602 (phone: 801-422-8717; email: \{mjg82,a,k\}@cs.byu.edu).}

### 2010-04-08 honors_thesis/journal_paper/paper.tex

At each iteration of the algorithm, the position $\ppos_t$ and velocity
$\pvel_t$ of each particle are updated as follows:
\begin{align}
\nonumber
	\pvel_{t+1} &=
		\constriction \bigl[ \pvel_t
			+ \pcoeff\pURand_{t}\otimes(\pbest_{t} - \ppos_{t}) \\
\label{eq:velupdate}
			& \quad \quad \quad \, + \ncoeff\nURand_{t}\otimes(\nbest_{t} - \ppos_{t})
		\bigr] \\
\label{eq:posupdate}
	\ppos_{t+1} &= \ppos_{t} + \pvel_{t+1}
\end{align}
where \( \pURand_{t} \) and \( \nURand_{t} \) are vectors of independent random
numbers drawn from a standard uniform distribution, the \( \otimes \) operator
is an element-wise vector multiplication, $\pbest$ (called personal best) is
the best position the current particle has seen, and $\nbest$ (called
neighborhood best) is the best position the neighbors of the current particle
have seen~\cite{bratton-2007-defining-a-standard-for-pso}.  \( \ncoeff \), \( \pcoeff \), and \(
\constriction \) are parameters with prescribed values required to ensure
convergence (2.05, 2.05, and .73, respectively)~\cite{clerc-2002-constricted-pso}.

There are many ways of defining the neighbors of a particle.  Changing the
neighborhood topology has a significant effect on the performance of the
algorithm and this effect varies widely by function type.  The two most common
topologies used in the literature are the Ring topology and the Complete
topology~\cite{bratton-2007-defining-a-standard-for-pso}.  In the Ring topology, each particle has one
neighbor to either side of it; in the Complete topology, every particle is a
neighbor to every other particle.  In all topologies a particle is also a
neighbor to itself in that its own position and value are considered when
updating the particle's neighborhood best, $\nbest$.  Thus with $p$ particles,
using the Ring topology each particle with index $i$ has three neighbors:
$i-1$, $i$ (itself), and $i+1$.  With the Complete topology, each particle has
$p$ neighbors.

>>>>

At each iteration of the algorithm, the position $\ppos_t$ and velocity
$\pvel_t$ of each particle are updated as follows:
\begin{align}
\nonumber
	\pvel_{t+1} &=
		\constriction \bigl[ \pvel_t
			+ \pcoeff\pURand_{t}\otimes(\pbest_{t} - \ppos_{t}) \\
\label{eq:velupdate}
			& \quad \quad \quad \, + \ncoeff\nURand_{t}\otimes(\nbest_{t} - \ppos_{t})
		\bigr] \\
\label{eq:posupdate}
	\ppos_{t+1} &= \ppos_{t} + \pvel_{t+1}
\end{align}
where \( \pURand_{t} \) and \( \nURand_{t} \) are vectors of independent random
numbers drawn from a standard uniform distribution, the \( \otimes \) operator
is an element-wise vector multiplication, $\pbest$ (called personal best) is
the best position the current particle has seen, and $\nbest$ (called
neighborhood best) is the best position the neighbors of the current particle
have seen~\cite{bratton-2007-defining-a-standard-for-pso}.  The parameters \( \ncoeff \), \( \pcoeff \),
and \( \constriction \) are given prescribed values required to ensure
convergence (2.05, 2.05, and .73, respectively)~\cite{clerc-2002-constricted-pso}.

Changing the
neighborhood topology has a significant effect on the performance of the
algorithm and this effect varies widely by function type.  The two most common
topologies used in the literature are the Ring topology and the Complete
topology~\cite{bratton-2007-defining-a-standard-for-pso}.  In the Ring topology, each particle has one
neighbor to either side of it; in the Complete topology, every particle is a
neighbor to every other particle.  In all topologies a particle is also a
neighbor to itself in that its own position and value are considered when
updating the particle's neighborhood best, $\nbest$.  Thus with $p$ particles,
using the Ring topology each particle with index $i$ has three neighbors:
$i-1$, $i$ (itself), and $i+1$.  With the Complete topology, each particle has
$p$ neighbors.
